Coherent optical association of single molecules

### 2020-08-28 paper.tex
Refinement

For atoms in the motional ground state in the tweezer, the average distance between the two atoms is $...$. However, for the ground rovibrational molecule, the bond length is only $...$. The size mismatch between the initial and final state causes a very small wavefunction overlap between the initial and final state, \todo{overlap is always 0, the accurate description here is the product of wavefunction overlap through any reasonable intermediate state, or the density-density correlation which serves as a reasonable estimate of the matrix element through different pathways} which poses the biggest challege for for coherent creation of the molecule. Because of this, it is necessary to use a intermediate state with a size in between the initial and final state and accomplish the transfer in two steps, each with improved wavefunction overlap.

@@

Even with the first step transfer to a weakly bond molecular state, it is still a challenge to achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state. For this reason, previous experiments also use weakly bond molecular excited states for the Raman transition. However, for a typical molecular potential, vibrationally excited states have a smaller spacing between neighboring states which limits the detuning for the Raman transition and increases the scattering. Moreover, there is also a significant scattering process from the excited atomic states due to the strong coupling with the weakly bond molecular ground state. Such scattering process is proportional to $1/\delta^2$ from the desociation threshold which is also much stronger for more weakly bound states. (combining these factors, confirm with figure 1 Rabi rate vs scattering rate calculation). Because of this, we use a deeply bound molecular excited state to drive the Raman transition.

>>>>

For atoms in the motional ground state in the tweezer, the average distance between the two atoms is $...$. However, for the ground rovibrational molecule, the bond length is only $...$. The size mismatch between the initial and final state causes a very small wavefunction overlap between them, \todo{overlap is always 0, the accurate description here is the product of wavefunction overlap through any reasonable intermediate state, or the density-density correlation which serves as a reasonable estimate of the matrix element through different pathways} which poses the biggest challege for for coherent creation of the molecule. Because of this, it is necessary to use a intermediate state with a size in between the initial and final states and accomplish the transfer in two steps, each with improved wavefunction overlap.

@@

Even with the first step transfer to a weakly bond molecular state, it is still a challenge to achieve high Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
For this reason, previous experiments also use weakly bond molecular excited states in the Raman transition.
However, this choice of state also increases the scattering during the transfer process for two reasons.
Firstly, since for a typical molecular potential the spacing between states decreases with increasing vibrational levels,
a weakly bond excited molecular state limits the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
Secondly, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
The rate of such scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold,
which further increases the scattering rate for a weakly bond excited state.
Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings.
As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, the weakly bond state also has a much higher scattering rate
and ultimately a smaller Rabi frequency to scattering at the optimal detuning. Based on this calculation, we use a deeply bound molecular excited state to drive the Raman transition.
